Learning Discrete Bayesian Networks from Continuous Data

### 2016-10-17 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
update abs&intro
minor

Learning Bayesian networks from raw data can help users to interpret the relations between variables and acquire knowledge without field-specific experts.
While real data often contains a mixture of discrete and continuous-valued variables, many Bayesian network structure learning algorithms assume all random variables are discrete. 
Thus, continuous variables are often discretized while learning a Bayesian network. 
However, the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
Empirical demonstrations show that the proposed method is superior to the classic method.
In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.

@@

The second approach is to use nonparametric distributions, such as particle representations and Gaussian processes \citep{Ickstadt_2010}.
Unlike parametric methods, nonparametric methods can often fit any underlying probability distribution given sufficient data.
Parametric models have a fixed number of parameters, whereas the number of parameters in a nonparametric model grow with the amount of training data.
%Inference algorithms on nonparametric models can be also inefficient.

The third approach is discretization.
Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
These methods learn for the best discretization policy for a continuous attribute by considering its interaction with a class variable.
It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interactions and dependencies between variables in Bayesian networks introduce complexity.
%The discretization of a variable in a network requires considering the impact on the variable's Markov blanket.
Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.

@@

% The probability of the data given the model typically increases with the number of discretization intervals, and the model prior is chosen to decrease with the number of discretization intervals
% Maximizing the model likelihood thus requires a trade-off in the number of discretization intervals.

%Bayesian methods select the model with maximum posterior probability given the data, %$P(\textit{Model} \mid \textit{Data})$.
%An application of Bayes' rule and constant $P(\textit{Data})$ shows that this is %equivalent to maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid %\textit{Model})}$, where $P(\textit{Model})$ is a prior over models and ${P(\textit{Data} %\mid \textit{Model})}$ is the data likelihood.
%The data likelihood usually increases with the number of discretization intervals, as %more intervals allow for richer representations.
%The prior is chosen to influence the relative merit between models, and for %discretization policies the prior is negatively correlated with the number of %discretization intervals to favor simpler models and prevent overfitting.
%Maximizing ${P(\textit{Model}) \cdot P(\textit{Data} \mid \textit{Model})}$ thus requires %a trade-off when determining the number of discretization intervals.

>>>>

Learning Bayesian networks from raw data can help interpret the variable iterrelationships and structure without relying on field-specific experts.
While real data often contains a mixture of discrete and continuous-valued variables, many Bayesian network structure learning algorithms assume all random variables are discrete.
Thus, continuous variables are often discretized when learning a Bayesian network.
However, the choice of discretization policy has significant impact on the accuracy, speed, and interpretability of the resulting models.
This paper introduces a principled Bayesian discretization method for continuous variables in Bayesian networks with quadratic complexity instead of the cubic complexity of other standard techniques.
Empirical demonstrations show that the proposed method is superior to the established minimum description length algorithm.
In addition, this paper shows how to incorporate existing methods into the structure learning process to discretize all continuous variables and simultaneously learn Bayesian network structures.

@@

The second approach is to use nonparametric distributions, such as particle representations and Gaussian processes \citep{Ickstadt_2010}.
Unlike parametric methods, nonparametric methods can often fit any underlying probability distribution given sufficient data.
Parametric models have a fixed number of parameters, whereas the number of parameters in a nonparametric model grow with the amount of training data.

The third approach is discretization.
Automated discretization methods have been studied in machine learning and statistics for many years \citep{Dougherty_1995, Kerber_1992, Holte_1993, Fayyad_1993}, primarily for classification problems.
These methods learn the best discretization policy for a continuous attribute by considering its interaction with a class variable.
It is common to discretize all continuous variables before learning a Bayesian network structure to avoid having to consider variable interactions, as the interactions and dependencies between variables in Bayesian networks introduce complexity.
Prior work exists for discretizing continuous variables in naive Bayesian networks and tree-augmented networks \citep{Fried_naive}, but only a few discretization methods for general Bayesian networks have been proposed \citep{Friedman_1996, Kozlov_1997, Monti_1998, Steck_2007}.

@@
